Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex)

### 2016-05-29 code/Rmd/Mayo_RNASeq_Reprocessed.Rmd
Minor bug fix

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=10, fig.width=9, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1)], scale.=T, center = T)

# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(RESIDUAL.GENE_EXPRESSION[,-(1)])), method = "average")

>>>>

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=10, fig.width=9, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION, scale.=T, center = T)

# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(RESIDUAL.GENE_EXPRESSION)), method = "average")
